Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-13 paper/Paper.tex
replace service provider with Curator and update contracts

A minimum DAO funding goal and funding time-period are set as parameters in the DAO code prior to deployment. If the minimum funding amount is not reached at the close of the funding period, all ether is returned. After the funding period has ended, we denote the total ether raised by $\Xi_{\text{raised}}$ and the total amount of tokens created by $T_{\text{total}}$.

@@

A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely. An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act. For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether. Our proposed solution is implemented by limiting each individual DAO to a single service provider. This service provider controls the only account that can receive ether from the DAO, across all proposals. In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to. This gives the service provider of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.

Any token holder can make a proposal to vote for a new service provider. In effect, even a single token holder is able to both retrieve their remaining portion of ether and maintain their right to any future rewards associated to their previous contribution, as these will be sent to the new DAO automatically. Rewards are defined as any ether received by the DAO generated from products the DAO funded so far and are explained in further detail in section \ref{RewardToken}.

The process of choosing a new service provider is as follows:
Any token holder can submit a proposal for a new service provider. In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $7$ days.
This is $7$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss (on or off-chain) the new service provider and conduct a first vote that's non-binding. After this first vote, token holders can cast a second one to confirm its results. In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.

\section{Token Price} \label{TokenPrice}
DAO Token price increases over time. This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO. 
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
0.01 + 0.0005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
0.015 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.0005 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.

@@

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenSale'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenSale’ defines how the DAO token is purchased for ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from the service provider to the DAO could look like.
\end{multicols}

@@

The constructor \verb|TokenSale| initiates the token sale with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateSale|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed.

The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $P(t) \cdot 200$ , as described in section \ref{TokenPrice}.

The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

The function \verb|refund| can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.

The function \verb|divisor| is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.

@@

\end{verbatim}
\begin{multicols}{2}
The original contract used as a starting point for ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
\url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
Now we will define the member variables and functions one at a time.

@@

The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|curator|, \verb|extraBalance| and addresses in the whitelist. Only the \verb|curator| can add addresses to the whitelist.

@@

The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change in service providers.

@@

A single proposal has the parameters:
\begin{description}
 \item[recipient] The address where the \verb|amount| of wei will go to if the proposal is accepted.
 \item[amount] The amount of wei to transfer to \verb|recipient| if the proposal is accepted.
 \item[description] A plain text description of the proposal.
 \item[votingDeadline] A unix timestamp, denoting the end of the voting period.
 \item[open] A boolean which is false if the votes have already been counted, true otherwise.
 \item[proposalPassed] A boolean which is true if a quorum has been achieved with the majority approving the proposal.
 \item[proposalHash] A hash to check validity of a proposal. Equal to \verb|sha3(_recipient, _amount, _transactionData)|.
 \item[proposalDeposit] The deposit (in wei) the creator of a proposal has send to submit a proposal. It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam. Its minimal value is set when the contract is deploayed as constructor parameter. But the creator of the proposal can send any amount above this for the deposit. The proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal. The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO. 
 \item[newServiceProvider] A boolean which is true if this proposal assigns a new service provider.
 \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new service provider.
 \item[yea] Number of tokens in favor of the proposal.
 \item[nay] Number of tokens in opposed to the proposal.
 \item[votedYes] Simple mapping to check if a token holder has voted for it.
 \item[votedNo] Simple mapping to check if a token holder has voted against it.
 \item[creator] The address of the token holder that created the proposal.
\end{description}

@@

\subsubsection*{newProposal}
This function is used to create a new proposal. The arguments of the function are:
\begin{description}
 \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current service provider or an address on the whitelist \verb|allowedRecipients|).
 \item[amount] The amount of wei to be sent in the proposed transaction.
 \item[description] A string describing the proposal.
 \item[transactionData] The data of the proposed transaction.
 \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new service provider proposal.
 \item[newServiceProvider] A boolean defining whether this proposal is for a new service provider or not.
\end{description}
After checking the sanity of the proposal (see code), this function creates a proposal which is open for voting for a certain amount of time. The function will return a proposal ID which is used to vote.

@@

\subsubsection*{executeProposal}
This function can be called by anyone. It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new service provider, than it does nothing.
The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[transactionData] The data of the proposed transaction
\end{description}
The function checks whether the voting deadline has passed and that the \verb|transactionData| matches the proposal ID. Then it checks whether the quorum has been met (see Eq. \ref{minQuorum}) and if the proposal had a majority of support. If this is the case, it executes the proposal and refunds the 
proposal deposit. If the quorum has been achieved, but the proposal was declined by the majority of the voters, the proposal deposit is refunded and the proposal closes.

\subsubsection*{emergenyCloseProposal}
This is used in the case `executeProposal` fails because it throws (e.g. when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction). It can be called $5$ days after the voting deadline of the proposal passed. It will close the proposal.
\subsubsection*{splitDAO}
After a new service provider has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new service provider. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newServiceProvider] The address of the new service provider of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, ther may be remainders which stay with the DAO.

\subsubsection*{newContract}
This function can only be called by the DAO itself (through a proposal and a vote) and is used to move all remaining ether, as well as all rewardTokens to a new address. This is used to update the contract. The new address needs to be approved by the service provider.

@@

\subsubsection*{transferPaidOut}
This function is called to when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
\begin{equation}
 P = P_{\text{from}} \cdot T_{\text{amount}} / T_{\text{from}}
\end{equation}
Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ the amount of tokens owned by the \verb|from| address.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = T_{\text{sender}} \cdot \Xi_{\text{rewardAccount}} / T_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount| and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.

@@

\subsubsection*{getNewDAOAdress}
This is just a helper function to read the address of a newly created `split DAO`. It gets the proposal ID which was used for the split as input parameter and return the address of the new DAO.

\subsubsection*{isBlocked}
This function returns true when the address given as parameter is currently blocked to transfer tokens due to an ongoing vote it has participated in, otherwise it returns false.

@@

Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount| (a \verb|ManagedAccount| contract).
Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.

@@

Let’s assume that during the split, a fraction of DAO tokens, $X$, changes service providers and leaves the DAO. The new DAO created receives $X \cdot \Xi_{\text{DAO pre}}$, a portion of the remaining ether from the original DAO.
\begin{equation}
 \Xi_{\text{DAO post}} = (1 - X) \cdot \Xi_{\text{DAO pre}}
\end{equation}
Here $\Xi_{\text{DAO pre}}$ is the ether balance of the original DAO before the split and $\Xi_{\text{DAO post}}$ is the ether balance of the original DAO after the split.

@@

The original DAO tokens of the accounts that confirmed the new service provider are destroyed.
Hence:
\begin{equation}
 T_{\text{total post}}= (1 - X) \cdot T_{\text{total pre}}
\end{equation}

@@

    // End of token sale, in Unix time
    uint public closingTime;   
    // Minimum funding goal of the token sale, denominated in tokens
    uint public minValue;  
    // True if the DAO reached its minimum funding goal, false otherwise
    bool public isFunded;   
    // For DAO splits - if privateSale is 0, then it is a public sale, otherwise
    // only the address stored in privateSale is allowed to purchase tokens
    address public privateSale;
    // hold extra ether which has been paid after the DAO token price has increased
    ManagedAccount extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum funding goal and the 
    /// end of the Token Sale
    /// @param _minValue Token Sale minimum funding goal
    /// @param _closingTime Date (in Unix time) of the end of the Token Sale
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenSale(uint _minValue, uint _closingTime);

    /// @notice Buy Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient 
    function buyTokenProxy(address _tokenHolder) returns (bool success);

    /// @notice Refund `msg.sender` in the case the Token Sale didn't reach its 
    /// minimum funding goal
    function refund();

    /// @return the divisor used to calculate the token price during the sale
    function divisor() returns (uint divisor);

@@

    function buyTokenProxy(address _tokenHolder) returns (bool success) {
        if (now < closingTime && msg.value > 0 
        && (privateSale == 0 || privateSale == msg.sender)) {
            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[msg.sender] += msg.value;
            SoldToken(_tokenHolder, token);
            if (totalSupply >= minValue && !isFunded) {
                isFunded = true;
                FundingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

    function refund() noEther {
        if (now > closingTime && !isFunded) {
            // get extraBalance - will only succeed when called for the first time
            extraBalance.payOut(address(this), extraBalance.accumulatedInput());

            // execute refund
            if (msg.sender.call.value(weiGiven[msg.sender])()) {
                Refund(msg.sender, weiGiven[msg.sender]);
                totalSupply -= balances[msg.sender];
                balances[msg.sender] = 0;
                weiGiven[msg.sender] = 0;
            }
        }
    }

    function divisor() returns (uint divisor){
        // the number of (base unit) tokens per wei is calculated
        // as `msg.value` * 20 / `divisor`
        // the funding period starts with a 1:1 ratio
        if (closingTime - 2 weeks > now) return 20;
        // followed by 10 days with a daily price increase of 5%
        else if (closingTime - 4 days > now)
            return (20 + (now - (closingTime - 2 weeks)) / (1 days));
        // the last 4 days there is a constant price ratio of 1:1,5
        else return 30;
    }
}
\end{verbatim}
\subsection{DAO}\label{app:DAO}
\begin{verbatim}
contract DAOInterface {

    // Proposals to spend the DAO's ether or to choose a new service provider
    Proposal[] public proposals;
    // The quorum needed for each proposal is partially calculated by
    // totalSupply / minQuorumDivisor
    uint minQuorumDivisor;
    // The unix time of the last time quorum was reached on a proposal
    uint lastTimeMinQuorumMet;

    // Address of the service provider
    address public curator;
    // The whitelist: List of addresses the DAO is allowed to send money to
    mapping (address => bool) public allowedRecipients;

>>>>

A minimum DAO funding goal and funding time-period are set as parameters in the DAO code during to deployment. If the minimum funding amount is not reached at the close of the funding period, all ether is returned. After the funding period has ended, we denote the total ether raised by $\Xi_{\text{raised}}$ and the total amount of tokens created by $T_{\text{total}}$.

@@

A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely.
An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some could be unaware of the situation and fail to act.
For the DAO to be considered safe, it is required that inactive token holders must also be protected from losing their ether. Our proposed solution is implemented by limiting each individual DAO to a single curator.
This curator controls the list of addresses that can receive ether from the DAO, across all proposals.
This gives the curator of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new curator, which may result in a split of the DAO as described above.

Any token holder can make a proposal to vote for a new curator. In effect, even a single token holder is able to both retrieve their remaining portion of ether and maintain their right to any future rewards associated to their previous contribution, as these will be sent to the new DAO automatically. Rewards are defined as any ether received by the DAO generated from products the DAO funded so far and are explained in further detail in section \ref{RewardToken}.

The process of choosing a new curator is as follows:
Any token holder can submit a proposal for a new curator. In this case, no proposal deposit is required, because an attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $7$ days.
This is $7$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss (on or off-chain) the new curator and conduct a first vote that's non-binding. After this first vote, token holders can cast a second one to confirm its results. In the case a majority opts to  keep the original curator, the minority can either change their vote to keep the original curator in order to avoid a split, or inversely they can confirm their vote for a new curator and move their portion of the funds to a new DAO.

\section{Token Price} \label{TokenPrice}
DAO Token price increases over time. This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO. 
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $1.5 \: \Xi_c$ per base unit of DAO token.

@@

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenSale'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenSale’ defines how the DAO token is purchased for ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from a contractor to the DAO could look like.
\end{multicols}

@@

The constructor \verb|TokenSale| initiates the token sale with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateSale|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed. 
In order to interact with the contract the following functions can be used:

\subsubsection*{buyTokenProxy}
This function creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

\subsubsection*{refund}
This function can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.

\subsubsection*{divisor}
This function is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.

@@

\end{verbatim}
\begin{multicols}{2}
The original contract used as a starting point for the ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
\url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
Now we will define the member variables and functions one at a time.

@@

The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|curator|, \verb|extraBalance| and addresses in the whitelist. Only the \verb|curator| can add/remove addresses to/from the whitelist.

@@

The integer \verb|proposalDeposit| specifies the minimum deposit to be paid in wei for any proposal that does not include a change of the curator.

@@

A single proposal has the parameters:
\begin{description}
 \item[recipient] The address where the \verb|amount| of wei will go to if the proposal is accepted.
 \item[amount] The amount of wei to transfer to \verb|recipient| if the proposal is accepted.
 \item[description] A plain text description of the proposal.
 \item[votingDeadline] A unix timestamp, denoting the end of the voting period.
 \item[open] A boolean which is false if the votes have already been counted, true otherwise.
 \item[proposalPassed] A boolean which is true if a quorum has been achieved with the majority approving the proposal.
 \item[proposalHash] A hash to check validity of a proposal. Equal to \verb|sha3(_recipient, _amount, _transactionData)|.
 \item[proposalDeposit] The deposit (in wei) the creator of a proposal has send to submit a proposal. It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam. Its minimal value is set when the contract is deployed as constructor parameter. But the creator of the proposal can send any amount above this for the deposit. The proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal. The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO. 
 \item[newCurator] A boolean which is true if this proposal assigns a new curator.
 \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new curator.
 \item[yea] Number of tokens in favor of the proposal.
 \item[nay] Number of tokens opposed to the proposal.
 \item[votedYes] Simple mapping to check if a token holder has voted for it.
 \item[votedNo] Simple mapping to check if a token holder has voted against it.
 \item[creator] The address of the token holder that created the proposal.
\end{description}

@@

\subsubsection*{newProposal}
This function is used to create a new proposal. The arguments of the function are:
\begin{description}
 \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current curator or an address on the whitelist \verb|allowedRecipients|).
 \item[amount] The amount of wei to be sent in the proposed transaction.
 \item[description] A string describing the proposal.
 \item[transactionData] The data of the proposed transaction.
 \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new curator proposal.
 \item[newCurator] A boolean defining whether this proposal is for a new curator or not.
\end{description}
After checking the sanity of the proposal (see code), this function creates a proposal which is open for voting for a certain amount of time. The function will return a proposal ID which is used to vote.

@@

\subsubsection*{executeProposal}
This function can be called by anyone. It counts the votes, in order to check whether the quorum is met, and executes the proposal if it passed, unless it is a proposal for a new curator, than it does nothing.
The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[transactionData] The data of the proposed transaction
\end{description}
The function checks whether the voting deadline has passed and that the \verb|transactionData| matches the proposal ID. Then it checks whether the quorum has been met (see Eq. \ref{minQuorum}) and if the proposal had a majority of support. If this is the case, it executes the proposal and refunds the 
proposal deposit. If the quorum has been achieved, but the proposal was declined by the majority of the voters, the proposal deposit is refunded and the proposal closes.

\subsubsection*{emergenyCloseProposal}
This is used in the case `executeProposal` fails because it throws (e.g. when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction). It can be called $5$ days after the voting deadline of the proposal passed. It will close the proposal.
\subsubsection*{splitDAO}
After a new curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new curator. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newCurator] The address of the new curator of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, there may be remainders which stay with the DAO.

\subsubsection*{newContract}
This function can only be called by the DAO itself (through a proposal and a vote) and is used to move all remaining ether, as well as all rewardTokens to a new address. This is used to update the contract. The new address needs to be approved by the curator.

@@

\subsubsection*{transferPaidOut}
This function is called when making any transfer of DAO tokens using \verb|transfer| or \verb|transferFrom| and it updates the array \verb|paidOut| to track the amount of rewards which has been paid out already, $P$, and is calculated as follows:
\begin{equation}
 P = P_{\text{from}} \cdot T_{\text{amount}} / T_{\text{from}}
\end{equation}
Here $P_{\text{from}}$ is the total amount of ether which has been paid out to the \verb|from| address (the sender), $T_{\text{amount}}$ is the amount of tokens to be transferred and $T_{\text{from}}$ the amount of tokens owned by the \verb|from| address.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to the address given as a parameter.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = T_{\text{sender}} \cdot \Xi_{\text{rewardAccount}} / T_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount| and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder address, which is given as a parameter. The reward tokens are further elaborated in section \ref{split}.

@@

\subsubsection*{getNewDAOAdress}
This is just a helper function to read the address of a newly created `split DAO`. It gets the proposal ID which was used for the split as input parameter and returns the address of the new DAO.

\subsubsection*{isBlocked}
This function returns true when the address given as parameter is currently blocked to transfer tokens due to an ongoing vote it has participated in, otherwise it returns false. It also unblocks the tokens in the case the voting deadline of the proposal is over.

@@

Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount| (a \verb|ManagedAccount| contract) and keeps track of the payouts in \verb|DAOpaidOut|.
Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.

@@

Let’s assume that during the split, a fraction of DAO tokens, $X$, changes the curator and leaves the DAO. The new DAO created receives $X \cdot \Xi_{\text{DAO pre}}$, a portion of the remaining ether from the original DAO.
\begin{equation}
 \Xi_{\text{DAO post}} = (1 - X) \cdot \Xi_{\text{DAO pre}}
\end{equation}
Here $\Xi_{\text{DAO pre}}$ is the ether balance of the original DAO before the split and $\Xi_{\text{DAO post}}$ is the ether balance of the original DAO after the split.

@@

The original DAO tokens of the accounts that confirmed the new curator are destroyed.
Hence:
\begin{equation}
 T_{\text{total post}}= (1 - X) \cdot T_{\text{total pre}}
\end{equation}

@@

    // End of token sale, in Unix time
    uint public closingTime;
    // Minimum fueling goal of the token sale, denominated in ether
    uint public minValue;
    // True if the DAO reached its minimum fueling goal, false otherwise
    bool public isFueled;
    // For DAO splits - if privateSale is 0, then it is a public sale, otherwise
    // only the address stored in privateSale is allowed to purchase tokens
    address public privateSale;
    // hold extra ether which has been paid after the DAO token price has increased
    ManagedAccount public extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum fueling goal and the
    /// end of the Token Sale
    /// @param _minValue Token Sale minimum fueling goal
    /// @param _closingTime Date (in Unix time) of the end of the Token Sale
    /// @param _privateSale Zero means that the sale is public.  A non-zero
    /// address represents the only address that can buy Tokens (the address
    /// can also buy Tokens on behalf of other accounts)
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenSale(
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateSale
    //  );

    /// @notice Buy Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient
    /// @return Whether the purchase was successful
    function buyTokenProxy(address _tokenHolder) returns (bool success);

    /// @notice Refund `msg.sender` in the case the Token Sale didn't reach its
    /// minimum fueling goal
    function refund();

    /// @return The divisor used to calculate the token price during the sale
    function divisor() returns (uint divisor);

@@

    function buyTokenProxy(address _tokenHolder) returns (bool success) {
        if (now < closingTime && msg.value > 0
            && (privateSale == 0 || privateSale == msg.sender)) {

            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[_tokenHolder] += msg.value;
            SoldToken(_tokenHolder, token);
            if (totalSupply >= minValue && !isFueled) {
                isFueled = true;
                FundingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

    function refund() noEther {
        if (now > closingTime && !isFueled) {
            // Get extraBalance - will only succeed when called for the first time
            extraBalance.payOut(address(this), extraBalance.accumulatedInput());

            // Execute refund
            if (msg.sender.call.value(weiGiven[msg.sender])()) {
                Refund(msg.sender, weiGiven[msg.sender]);
                totalSupply -= balances[msg.sender];
                balances[msg.sender] = 0;
                weiGiven[msg.sender] = 0;
            }
        }
    }

    function divisor() returns (uint divisor) {
        // The number of (base unit) tokens per wei is calculated
        // as `msg.value` * 20 / `divisor`
        // The fueling period starts with a 1:1 ratio
        if (closingTime - 2 weeks > now) {
            return 20;
        // Followed by 10 days with a daily price increase of 5%
        } else if (closingTime - 4 days > now) {
            return (20 + (now - (closingTime - 2 weeks)) / (1 days));
        // The last 4 days there is a constant price ratio of 1:1.5
        } else {
            return 30;
        }
    }
}
\end{verbatim}
\subsection{DAO}\label{app:DAO}
\begin{verbatim}
contract DAOInterface {

    // The amount of days for which people who try to participate in the sale
    // by calling the fallback function will still get their money back
    uint constant saleGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal can be closed (used in the case `executeProposal`
    // fails because it throws)
    uint constant executeProposalPeriod = 5 days;
